Automated Topic Naming

### 2012-01-15 ese/ese.tex
- [X] Talk about Treude's concernlines      In the related work part you mention ConcernLines by Truede. Could you      be more precise and specify where the tags come from (source code, cvs      logs, ...)

Another approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} used Latent Semantic Indexing (LSI)
to identify commonly occurring concerns for software maintenance. 
The
concerns are given by the user, and LSI is used to retrieve them from
a corpus. 
Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
With ConcernLines, Treude et al.~\cite{treude09cl} showed tag occurrence
using colour and intensity. 
They mined
developer created tags 
%change request tags (such as `milestone 3') and used these 
in order to analyze the evolution of a single product.
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.

>>>>

Another approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} used Latent Semantic Indexing (LSI)
to identify commonly occurring concerns for software maintenance. 
The
concerns are given by the user, and LSI is used to retrieve them from
a corpus. 
Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
With ConcernLines, Treude et al.~\cite{treude09cl} showed tag occurrence
using colour and intensity. 
They mined
developer created 
change request tags from IBM Jazz
repositories and used these 
in order to analyze the evolution of a single product.
Change requests in Jazz allow for users to annotate each change
request and check-in with tags such as ``ui'', ``usability'' or
``milestone 3''. 
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.
